Finding shortest and closest vectors in a lattice of Voronoi's first kind

### 2015-07-02 talk/presentation.tex
mino

\title{Finding shortest and closest vectors in a lattice of Voronoi's first kind}
\author{Robby McKilliam \\
%\vspace{0.2cm}
Alex Grant \\ Vaughan Clarkson \\
\vspace{0.7cm}
{\small
Institute for Telecommunications Research \\ University of South Australia 
\\ \vspace{0.2cm}
School of Information Technology and Electrical Engineering \\ The University of Queensland
}
}

@@

\frame{
\frametitle{The shortest vector problem}
\begin{itemize}
\item Computing a short vector is called the \term{shortest vector problem}.
\item NP-hard for arbitrary lattices.
\end{itemize}
}

\frame{
\frametitle{The shortest vector problem}
Longstanding applications in computer science:
\begin{itemize}
\item integer programming {\tiny (Lenstra~et.~al. 1983, Kannan 1987)}
\item the factoring of polynomials over rationals {\tiny (Lenstra~et.~al. 1982)}
\item check solvability by radicals {\tiny (Landau and Miller 1985)}
\item solving low density subset sum problems {\tiny (Coster~et.~al. 1992)}
\end{itemize}
}

\frame{
\frametitle{The shortest vector problem}
Central problem in modern cryptography enabling:
\begin{itemize}
\item efficient public key encryption {\tiny (Gentry~et.~al. 2008, Micciancio 2012)}
\item post quantum cryptography {\tiny (Perlner~et.~al. 2009, Guneysu 2014, Peikert 2014)}
\item efficient hash functions {\tiny (Peikert and Rosen 2006, Micciancio 2007)}
\item fully homomorphic encryption {\tiny (Gentry~et.~al. 2009, 2010)}
\end{itemize}
}

\frame{
\frametitle{The shortest vector problem}
Communications applications:
\begin{itemize}
\item minimum distance of lattice codes {\tiny (Conway and Sloane 1998, Erez~et.~al. 2004)}
\item capacity analysis of network codes {\tiny (Nazer and Gastpar 2011)}
\end{itemize}
}

\frame{
\frametitle{The shortest vector problem}
\begin{itemize}
\item NP-hard for arbitrary lattices.
\item Easier for specific lattices.
\item Short vectors are easy to find in the \term{root lattices} $\ints^n$, $A_n$, and $D_n$.
\item We will show that the problem is relatively easy to solve for lattices of \term{Voronoi's first kind}.
\end{itemize}
}

>>>>

\title{Finding shortest and closest vectors in a lattice of Voronoi's first kind}
\author{Robby McKilliam \\
%\vspace{0.2cm}
Alex Grant \\ Vaughan Clarkson \\
\vspace{0.7cm}
{\small
Institute for Telecommunications Research \\ School of Information Technology and Mathematical Sciences \\ University of South Australia 
\\ \vspace{0.2cm}
School of Information Technology and Electrical Engineering \\ The University of Queensland
}
}

@@

\frame{
\frametitle{The shortest vector problem}
\begin{itemize}
\item Computing a short vector is called the \term{shortest vector problem}.
\item Applications in cryptography and number theory.
\item NP-hard for arbitrary lattices.
\item Easier for specific lattices.
\item Short vectors are easy to find in the \term{root lattices} $\ints^n$, $A_n$, and $D_n$.
\item We will show that the problem is relatively easy to solve for lattices of \term{Voronoi's first kind}.
\end{itemize}
}
